### 2020-10-06 README.Rmd
Change species for SCBI example

```{r, eval = run_scbi}
posterior_plots_scbi <- plot_posterior_parameters(
  posterior_param = posterior_param_scbi,
  sp_to_plot = c("caca", "litu", "cagl", "cato")
)
```

```{r, eval = run_scbi}
posterior_plots_scbi[["lambda"]]
```

>>>>

```{r, eval = run_scbi}
posterior_plots_scbi <- plot_posterior_parameters(
  posterior_param = posterior_param_scbi,
  sp_to_plot = c("quru", "litu", "cagl", "cato")
)
```

```{r, eval = run_scbi}
posterior_plots_scbi[["lambda"]]
#comment to change
```
